### 2016-08-11 ms/ms.tex
finished writing results and methods

\documentclass[12pt]{article} 
\usepackage[pdftex]{graphicx}
\usepackage{natbib} 
\usepackage{color}
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{verbatim}
\usepackage{mathpazo} 
\usepackage{setspace}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{lscape}
\usepackage{fancyhdr}
\usepackage[normalem]{ulem} 
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage{xr}
\usepackage{paralist}
\usepackage{xr}
\externaldocument{SI}
\hypersetup{colorlinks=true, linkcolor=black, citecolor=black}
\RequirePackage{lineno}

@@

We surveyed plant-pollinator interaction networks of assembling
hedgerows (N=5), as well as in two types of non-assembling communities
to serve as controls: unrestored, weedy field margins (N=XX) and
established hedgerows (greater than 10 years since planting,
N=XX). The sites were located in the Central Valley of California in
Yolo, Colusa and Solano Counties. This area is comprised of
intensively managed agriculture -- primarily monocultures of
conventional row crops, vineyards and orchards. Hedgerows we planted
along field margins where they do not remove valuable land from
production, and are ca. 3--6m wide and approximately 350m long and
border large (ca.\ 30--hectare) crop fields. Hedgerows consist of
native, perennial, shrub and tree plantings including \textit{Rosa
  californica}, \textit{Cercis occidentalis}, \textit{Ceanothus spp.},
\textit{Heteromeles arbutifolia}, \textit{Sambucus mexicana},
\textit{Eriogonum spp.}, \textit{Baccharis spp.}, \textit{Salvia
  spp}. and others \citep{kremen-2015-602, mgonigle-2015-x}. The mean
distance between monitoring sites was 15 km, and the minimum distance
between sites of the same type sampled in the same year was 2 km.  The
entire area surveyed spanned almost 300 km$^2$. The crop fields
adjacent to all sites were similarly managed as intensive, high-input
monoculture.

Monitoring began in 2006 and continued through 2015. Sampling of the
assembling hedgerows began the year before the area was restored. For
logistical reasons, no sampling of assembling hedgerows was conducted
in 2010. Sites were sampled between two and five times per year (Table
XX). In each round of sampling, the order in which sites were sampled
was randomized. Surveys were conducted under sunny conditions when the
temperature was above $21^{\circ}\mathrm{C}$ and wind speed was below
$2.5$ meters/second.

Flower-visitors to plants in hedgerows and unrestored controls were
netted for one hour of active search time (the timer was paused when
handling specimens). Honeybees (\textit{Apis mellifera}) were not
collected because their abundance is determined largely by the
placement of hives throughout the region by bee-keepers. All other
insect flower visitors that touched the reproductive parts of the
flower were collected; however, here we focus only on wild bees and
syrphids (representing XX and XX percent of records, respectively),
the most abundant and effective pollinators in the system (C. Kremen,
A. Klein and L. Morandin, unpublished data). Bee and syrphid specimens
were identified to species (or morpho-species for some bee specimens
in the genera \textit{Nomada} and \textit{Sphecodes}) by expert
taxonomists.

@@

Once the GHRG model has been fit to the networks, we determine whether
a change point occurred between two time slices. To detect a change
point, we compare the fit of two models -- one where a change point
had occurred between two networks, and one where no change occurred --
using posterior Bayes factors. We chose a sliding window of length,
$w$, of four, within which to find change points. Larger windows allow
for more gradual changes, and four was the maximum possible with our
maximum of nine years of data. Lastly, to calculate a $p$-value for
the Bayes factors, we use parametric bootstrapping to numerically
estimate the null distribution \citep{peel2014detecting}. The change
point analysis was carried out using code published online by L.~Peel.

We next test whether the change points occurring in maturing hedgerows
were a component of the assembly process or a product of environmental
shifts that lead to network reorganizations in all types of
communities. We model the number of change points as successes and the
total number of years each site was sampled as trails, and use a
generalized linear model with Binomial error to test whether the
probability of a change point occurring varied by site type. For the
non-assembling hedgerows and weedy field margins, only sites with five
or greater years of sampling was included in this analysis.

@@

We calculate species persistence as the proportion of the surveys a
pollinator was observed. Species observed consistently within and
between years are thus maximally persistent. Weighted species degree
is calculated from interaction observations observed in more extensive
data-set from Yolo County (approx.~ 18000 interaction records) that
included both the data included in this study and additional data from
sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}.%% does this make sense to
                                %% calculate from an independent data set?
To represent the the variability of species within networks, we
computed the coefficient of variation of weighted closeness at each
site through time. Closeness describes the centrality of a species in
the network by calculating path lengths to other vertices (species) in
the graph. We used linear mixed models to test whether the variability
of species closeness values was related to the persistence or degree
of that species. We included random effects for species, as well as
site. We focused on the pollinator species because the hedgerow
flowers are planted and thus are not directly assembling. Because
degree and persistence were strongly correlated, ($\rho = 0.84$,
$p$-value $<$ $2*10^{-16}$), each explanatory variable was included in
the model separately.

\subsection*{Temporal changes in interaction patterns}
The changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main topologies ---
modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. Modular community
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Communities in the
network may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid (i.e., preferential
attachment), nestedness would increase through time. Lastly, if the
network is accumulating specialist species or species are beginning to
limit their interaction niche breath as the network assembles, this
would lead to an increase in the network-level specialization
\citep{bluthgen-2006-9}. To test whether network modularity,
nestedness or specialization changed linearly with assembly, we used
linear mixed models with the descriptive network metrics as the
response variable, year of assembly as the explanatory variable, and
random effects of site and year.

@@

Lastly, we test the changes in interaction patterns associated with
network assembly affect the robustness. First, following
\cite{Memmott2004}, we simulate the extinction of plant species the
subsequent extinction cascades of pollinator species. Because the
reproduction of plant species if facilitated by active restoration
efforts, it is unlikely the extinction of pollinators would effect
plant populations in the hedgerows. However, plants ceasing to bloom,
for example in response to drought, will likely effect the pollinators
that depend on them. Plants species were eliminated based on their
degree or abundance, and the number of pollinators that secondarily
went extinct is calculated. The area below the extinction curve is
used as a measure of network robustness \citep{Memmott2004}.

@@

\section*{Results}
\label{sec:results}
\subsection*{Change point analysis}
\subsubsection*{Identifying change points}

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{../analysis/changePoint/plotting/networks.pdf}
  \caption{XXX}
  \label{fig:changePoints}
\end{figure}
\clearpage

@@

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{../analysis/variability/figures/cv/occ_degree.pdf}
  \caption{XXX}
  \label{fig:cv}
\end{figure}
\clearpage

\subsection*{Network structure}

\begin{figure}
  \centering
  \includegraphics[width=.4\textwidth]{../analysis/networkLevel/figures/baci.pdf}
  \caption{XXX}
  \label{fig:baci}
\end{figure}
\clearpage

>>>>

\documentclass[12pt]{article} 
\usepackage[pdftex]{graphicx}
\usepackage{natbib} 
\usepackage{color}
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{verbatim}
\usepackage{mathpazo} 
\usepackage{setspace}
\usepackage{multirow}
\usepackage{fullpage}
\usepackage{lscape}
\usepackage{fancyhdr}
\usepackage[normalem]{ulem} 
\usepackage{hyperref}
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{times}
\usepackage{textcomp}
\usepackage{xr}
\usepackage{etoolbox}
\usepackage{filecontents}
\usepackage{url}
\externaldocument{SI}
\hypersetup{colorlinks=true, linkcolor=black, citecolor=black}
\RequirePackage{lineno}

@@

We surveyed plant-pollinator interaction networks of assembling
hedgerows (N=5), as well as in two types of non-assembling communities
to serve as controls: unrestored, weedy field margins (N=19) and
established hedgerows (greater than 10 years since planting,
N=29). The sites were located in the Central Valley of California in
Yolo, Colusa and Solano Counties. This area is comprised of
intensively managed agriculture -- primarily monocultures of
conventional row crops, vineyards and orchards. Hedgerows we planted
along field margins where they do not remove valuable land from
production, and are ca. 3--6m wide and approximately 350m long and
border large (ca.\ 30--hectare) crop fields. Hedgerows consist of
native, perennial, shrub and tree plantings including \textit{Rosa
  californica}, \textit{Cercis occidentalis}, \textit{Ceanothus spp.},
\textit{Heteromeles arbutifolia}, \textit{Sambucus mexicana},
\textit{Eriogonum spp.}, \textit{Baccharis spp.}, \textit{Salvia
  spp}. and others \citep{kremen-2015-602, mgonigle-2015-x}. The mean
distance between monitoring sites was 15 km, and the minimum distance
between sites of the same type sampled in the same year was 2 km.  The
entire area surveyed spanned almost 300 km$^2$. The crop fields
adjacent to all sites were similarly managed as intensive, high-input
monoculture.

Monitoring began in 2006 and continued through 2015. Sampling of the
assembling hedgerows began the year before the area was restored. For
logistical reasons, no sampling of assembling hedgerows was conducted
in 2010. Sites were sampled between two and five times per year
(Tables S1-S3). In each round of
sampling, the order in which sites were sampled was
randomized. Surveys were conducted under sunny conditions when the
temperature was above $21^{\circ}\mathrm{C}$ and wind speed was below
$2.5$ meters/second.

Flower-visitors to plants in hedgerows and unrestored controls were
netted for one hour of active search time (the timer was paused when
handling specimens). Honeybees (\textit{Apis mellifera}) were not
collected because their abundance is determined largely by the
placement of hives throughout the region by bee-keepers. All other
insect flower visitors that touched the reproductive parts of the
flower were collected; however, here we focus only on wild bees and
syrphids (representing 49 and 19 percent of records, respectively),
the most abundant and effective pollinators in the system (C. Kremen,
A. Klein and L. Morandin, unpublished data). Bee and syrphid specimens
were identified to species (or morpho-species for some bee specimens
in the genera \textit{Nomada} and \textit{Sphecodes}) by expert
taxonomists.

@@

Once the GHRG model has been fit to the networks, we determine whether
a change point occurred between two time slices. To detect a change
point, we compare the fit of two models -- one where a change point
had occurred between two networks, and one where no change occurred --
using posterior Bayes factors. We chose a sliding window of length,
$w$, of four, within which to find change points. Larger windows allow
for more gradual changes, and four was the maximum possible with our
maximum of nine years of data. Lastly, to calculate a $p$-value for
the Bayes factors, we use parametric bootstrapping to numerically
estimate the null distribution \citep{peel2014detecting}. The change
point analysis was carried out using code published online by
L.~Peel. Analyses we conducted in Python 3.4.

We next test whether the change points occurring in maturing hedgerows
were a component of the assembly process or a product of environmental
shifts that lead to network reorganizations in all types of
communities. We model the number of change points as successes and the
total number of years each site was sampled as trails, and use a
generalized linear model with Binomial error to test whether the
probability of a change point occurring varied by site type. For the
non-assembling hedgerows and weedy field margins, only sites with five
or greater years of sampling was included in this analysis. All
statistical analysis were conducted in R 3.2.3 \citep{R}.

@@

We calculate species persistence as the proportion of the surveys a
pollinator was observed. Species observed consistently within and
between years are thus maximally persistent. Weighted species degree
is calculated from interaction observations observed in more extensive
data-set from Yolo County (approx.~ 18000 interaction records) that
included both the data included in this study and additional data from
sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}.%% does this make sense to
%% calculate from an independent data set?
To represent the the variability of species within networks, we
computed the coefficient of variation of weighted closeness at each
site through time. Closeness describes the centrality of a species in
the network by calculating path lengths to other vertices (species) in
the graph. We used linear mixed models to test whether the variability
of species closeness values was related to the persistence or degree
of that species \citep{lme4, lmetest}. We included random effects for
species, as well as site. We focused on the pollinator species because
the hedgerow flowers are planted and thus are not directly
assembling. Because degree and persistence were strongly correlated,
($\rho = 0.84$, $p$-value $<$ $2*10^{-16}$), each explanatory variable
was included in the model separately. Because a linear increase in
closeness, as might be expected with assembly by preferential
attachment, would lead to a high variability in closeness scores, we
also test whether closeness increases through time.

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
The changing points in network structure may contribute to the
reorganization of the assembling networks into predictable interaction
patterns. Pollination networks exhibit two main topologies ---
modularity \citep[e.g.,][]{Olesen2007} and nestedness
\citep[e.g.,][]{Bascompte2006, Bascompte2003}. Modular community
interactions are insular, occurring within separate groups or
``modules'' more often than between modules. Communities in the
network may fragment as the network assembles, enhancing
modularity. Conversely, nested networks are like pyramid of
interactions, where there are some species that interact with many
species, other species that interact with a subset of those species,
and so on. If species entering the network tend to interact with the
generalist base of the network pyramid (i.e., preferential
attachment), nestedness would increase through time. Lastly, if the
network is accumulating specialist species or species are beginning to
limit their interaction niche breath as the network assembles, this
would lead to an increase in the network-level specialization
\citep{bluthgen-2006-9}. To test whether network modularity,
nestedness or specialization changed linearly with assembly, we used
linear mixed models with the descriptive network metrics as the
response variable, year of assembly as the explanatory variable, and
random effects of site and year.

@@

Lastly, we test whether the changes in interaction patterns associated
with network assembly affect the robustness. First, following
\cite{Memmott2004}, we simulate the extinction of plant species the
subsequent extinction cascades of pollinator species. Because the
reproduction of plant species if facilitated by active restoration
efforts, it is unlikely the extinction of pollinators would effect
plant populations in the hedgerows. However, plants ceasing to bloom,
for example in response to drought, will likely effect the pollinators
that depend on them. Plants species were eliminated based on their
degree or abundance, and the number of pollinators that secondarily
went extinct is calculated. The area below the extinction curve is
used as a measure of network robustness \citep{Memmott2004}.

@@

\section*{Results}
\label{sec:results}

Over eight years and $747$ samples, we collected and identified
$19,547$ wild bees and syrphids comprising $173$ species from $50$
genera. We observed $1,521$ unique interactions between plants and
pollinators.

\subsection*{Change point analysis}
\subsubsection*{Identifying change points}

The majority ($76\%$) of the sites tests underwent at least one
significant reorganization of interactions (Fig.~
\ref{fig:changePoints}). There were no consistent trends as to when
change points occurred within assembling hedgerows or across all sites,
except many site had changing points between year 2009 and 2011 (Fig.~
\ref{fig:changePoints}). In California, 2011 marked the beginning of a
multi year drought. In the assembling hedgerows were not sampled in
2010, so disentangling whether the changing points are due to skipping
a year of assembly or the drought is not impossible.

All five of the assembling hedgerows experienced changing points,
whereas only $40\%$ and $81\%$ of non-assembling hedgerows and field
margins, respectively, underwent significant interaction
reorganizations. Assembling hedgerows experienced significantly more
changing points than the non-assembling networks (difference in the
odds ratios between assembling and non-assembling networks $\pm$
$95\%$ CI, $3.316 \pm 1.314 8.572$, $p$-value= $0.0117$). Network
assembly following restoration is thus punctuated by more interaction
reorganizations than would be expected by environmental shifts that
would effect assembling and non-assembling networks equally.

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{../analysis/changePoint/plotting/networks.pdf}
  \caption{The network structure and changing points (vertical red
    lines) in assembling hedgerows and a representative sample of
    non-assembling hedgerows and weedy field margins. In each network,
    plants and pollinators are represented by green and yellow
    circles, respectively, weighted by their degree. Each species has
    has a consistent position in the network across years. In the
    assembling hedgerows, colored circles in the corner of each
    network represent the years post restoration.}
  \label{fig:changePoints}
\end{figure}
\clearpage

@@

In contradiction to the predictions of assembly by preferential
attachment, both pollinator persistence and degree were positively
related to network position variability. (ADD STATS IF KEEPING
RESULT).

\begin{figure}
  \centering
  \includegraphics[width=.8\textwidth]{../analysis/variability/figures/cv/occ_degree.pdf}
  \caption{The coefficient of variation of network position, as
    represented by closeness, plotted against pollinator persistence
    and degree. Points represents means for each species across sites.
    The solid line indicates the mean slope estimate and the dashed
    lines are the $95\%$ confidence intervals around the estimate. }
  \label{fig:cv}
\end{figure}
\clearpage

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
Network nestedness significantly increased with assembly (estimate of
the slope of nestedness through time $\pm$ standard error of the
estimate, $1.834 \pm 0.6142$, $p$-value=$0.022$, Fig.~
\ref{fig:baci}).  Modularity decreased (Fig.~ \ref{fig:baci}), though
the slope was not significantly different from zero (estimate of the
slope of modularity through time $\pm$ standard error of the estimate,
$-0.524$ $\pm$ $0.295$, $p$-value=$0.124$). Specialization remained
relatively constant (estimate of the slope of specialization through time
$\pm$ standard error of the estimate, $0.003$ $\pm$ $0.015$,
$p$-value=$0.827$).

\begin{figure}
  \centering
  \includegraphics[width=.7\textwidth]{../analysis/networkLevel/figures/baci.pdf}
  \caption{The change in nestedness, modularity, specialization and
    connectance as the networks assemble. The left panels represent
    $z$-scores. Scores greater than $\sim 2$ or less than $\sim -2$
    are significantly more or less structured than randomly assembled
    networks. Points are the value for each site at each year of
    assembly. The solid line indicates the mean slope estimate and the
    dashed lines are the $95\%$ confidence intervals around the
    estimate.}
  \label{fig:baci}
\end{figure}
\clearpage

\subsection*{Network robustness}
Assembly did not effect the robustness of the networks to species
extinction when species where removed incrementally by degree
(estimate of the slope of robustness through time $\pm$ standard error
of the estimate, $6*10^{-5} \pm 4*10^{-3}$, $p$-value=$0.987$) or
abundance ($0.001 \pm 0.003$, $p$-value=$0.65$, Fig.~ \ref{fig:rob}).

In contrast, the robustness of networks to perturbation, as measured
by the algebraic connectivity of the network, increased as the network
assembled (estimate of the slope of robustness through time $\pm$
standard error of the estimate, $0.6814 \pm 0.272$, $p$-value=$0.042$,
Fig.~ \ref{fig:rob}).

\begin{figure}
  \centering
  \includegraphics[width=.7\textwidth]{../analysis/networkLevel/figures/robustness.pdf}
  \caption{The robustness of networks to species extinction and
    perturbation. The robustness to species extinction is measured by
    incrementally removing species by degree, through removing
    species by abundance did not yield qualitatively different
    results. Points are the value for each site at each year of
    assembly. The solid line indicates the mean slope estimate and the
    dashed lines are the $95\%$ confidence intervals around the
    estimate.}
  \label{fig:rob}
\end{figure}
\clearpage
